Supplementary Materials for Openness and Computational Reproducibility in Plant Pathology: Where do we Stand and a Way Forward

### 2022-07-01 analysis/paper/paper.Rmd
Remove "abbreviation" and "year" from y-axis-tick-marks

```{r journal-parameters, echo=FALSE, message=FALSE, warning=FALSE, fig.cap='95% credible interval for the probability associated with the journal title for (A) computational materials (code) and (B) data being made readily available to the public. A test for equivalence was unable to detect any clear differences between *Phytopathology* and all other journals sharing computational materials (code). However, a test for equivalence found that *Molecular Plant Pathology* and *Phytopathologia Mediterranea* were more likely have data available than articles found in *Phytopathology*. Intervals in grey have a median value less than that of *Phytopathology*, the base level used for the analysis and articles in these journals could be less likely to share computational materials and data than articles published in *Phytopathology*. Intervals in black have a median value that is greater than that of *Phytopathlogy*, the base level for the analysis and articles in these journals could be more likely to share data or code than those found in *Phytopathology*.', cache=FALSE, fig.env='figure'}
a <- plot(parameters(m_f1)) +
  scale_colour_grey() +
  ggtitle("Code")

>>>>

```{r journal-parameters, echo=FALSE, message=FALSE, warning=FALSE, fig.cap='95% credible interval for the probability associated with the journal title for (A) computational materials (code) and (B) data being made readily available to the public. A test for equivalence was unable to detect any clear differences between *Phytopathology* and all other journals sharing computational materials (code). However, a test for equivalence found that *Molecular Plant Pathology* and *Phytopathologia Mediterranea* were more likely have data available than articles found in *Phytopathology*. Intervals in grey have a median value less than that of *Phytopathology*, the base level used for the analysis and articles in these journals could be less likely to share computational materials and data than articles published in *Phytopathology*. Intervals in black have a median value that is greater than that of *Phytopathlogy*, the base level for the analysis and articles in these journals could be more likely to share data or code than those found in *Phytopathology*.', cache=FALSE, fig.env='figure'}

a_y_labs <- rev(gsub("b_abbreviation", "", parameters(m_f1)$Parameter)[-c(1:2)])
a <- plot(parameters(m_f1)) +
  scale_y_discrete(labels = a_y_labs) +
  scale_colour_grey() +
  ggtitle("Code")

### 2022-07-01 analysis/supplementary materials/Supplementary Materials.Rmd
Remove "abbreviation" and "year" from y-axis-tick-marks

library("Reproducibility.in.Plant.Pathology")
packages <- c(
  "tidyverse",
  "bayesplot",
  "bayestestR",
  "brms",
  "extrafont",
  "flextable",
  "ggpubr",
  "here",
  "knitr",
  "officer",
  "pander",
  "posterior",
  "report",
  "tools"
)

@@

```{r journal-code-test, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Equivalence test for a model testing the effect of the publishing journal on articles\' supporting code availability."}
p <- plot(equivalence_test(m_f1))

@@

```{r journal-data-test, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Equivalence test for a model testing the effect of the publishing journal on articles\' supporting code availability."}
p <- plot(equivalence_test(m_f2))

@@

```{r year-code-test, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Equivalence test for a model testing the effect of the year of publication title on articles\' supporting code availability."}
p <- plot(equivalence_test(m_g1))

@@

```{r year-data-test, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Equivalence test for a model testing the effect of the year of publication on articles\' supporting data availability."}
p <- plot(equivalence_test(m_g2))

>>>>

library("Reproducibility.in.Plant.Pathology")
packages <- c(
  "tidyverse",
  "bayesplot",
  "bayestestR",
  "brms",
  "extrafont",
  "flextable",
  "ggpubr",
  "here",
  "knitr",
  "officer",
  "pander",
  "parameters",
  "posterior",
  "report",
  "tools"
)

@@

```{r journal-code-test, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Equivalence test for a model testing the effect of the publishing journal on articles\' supporting code availability."}
y_labs <- gsub("abbreviation", "", parameters(m_f1)$Parameter)
y_labs <- rev(gsub("b_", "", y_labs))
y_labs <- y_labs[c(21:22, 1:20)]

p <- plot(equivalence_test(m_f1)) +
    scale_y_discrete(labels = y_labs)

@@

```{r journal-data-test, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Equivalence test for a model testing the effect of the publishing journal on articles\' supporting code availability."}
y_labs <- gsub("abbreviation", "", parameters(m_f2)$Parameter)
y_labs <- rev(gsub("b_", "", y_labs))
y_labs <- y_labs[c(21:23, 1:20)]

p <- plot(equivalence_test(m_f2)) +
    scale_y_discrete(labels = y_labs)

@@

```{r year-code-test, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Equivalence test for a model testing the effect of the year of publication title on articles\' supporting code availability."}
y_labs <- gsub("year", "", parameters(m_g1)$Parameter)
y_labs <- rev(gsub("b_", "", y_labs))
y_labs <- y_labs[c(10:11, 1:9)]

p <- plot(equivalence_test(m_g1)) +
  scale_y_discrete(labels = y_labs)

@@

```{r year-data-test, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Equivalence test for a model testing the effect of the year of publication on articles\' supporting data availability."}
p <- plot(equivalence_test(m_g2)) +
  scale_y_discrete(labels = y_labs)
